2H SIP Taxonomy

### 2022-06-09 02_bacdive_taxonomy.Rmd
added .RDS extension
output data for supplemental dataset

```{r}
fatty_acids_wide_with_tax %>% saveRDS(file = "cache/bacdive_FA_wide")

fatty_acids_with_tax %>% saveRDS(file = "cache/bacdive_FA")

>>>>

```{r}
fatty_acids_wide_with_tax %>% saveRDS(file = "cache/bacdive_FA_wide.RDS")
write_csv(fatty_acids_wide_with_tax, file = "data_output/bacdive_FAs.csv")

fatty_acids_with_tax %>% saveRDS(file = "cache/bacdive_FA.RDS")
